How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2021-04-14 analysis/paper/paper.Rmd
Fixed wrong p value on rmd file

Figure \@ref(fig:volume-density-retouch) shows a strong pattern of artifacts from less dense assemblages having higher retouch frequencies while more dense assemblages have lower retouch frequencies (`r den_sp_ttest_str`), further showing a spectrum of site functions in this sample. As we saw for artifact density, there are no clear directional chronological trends in retouch frequencies. Assemblages containing stemmed points tend to have substantially fewer retouched pieces compared to assemblages without stemmed points (`r retouch_sp_ttest_str`).

>>>>

Figure \@ref(fig:volume-density-retouch) shows a strong pattern of artifacts from less dense assemblages having higher retouch frequencies while more dense assemblages have lower retouch frequencies (`r combined_retouch_density_ttest_str`), further showing a spectrum of site functions in this sample. As we saw for artifact density, there are no clear directional chronological trends in retouch frequencies. Assemblages containing stemmed points tend to have substantially fewer retouched pieces compared to assemblages without stemmed points (`r retouch_sp_ttest_str`).
